A Taxonomy of Twists of Supersymmetric Yang--Mills Theory -- Comments on Referee Report

### 2022-04-15 paper_journal_edits.tex
more corrections to earlier in the paper

The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief, the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.  That is, given a space $\mc F$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\mc F$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \mc F \cap^h_{T^*\mc F} \Gamma_{\d S}$ of the zero section in $T^*\mc F$ with the graph of $\d S$.  The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$ as a formal moduli problem.

@@

@@

\begin{example}
Suppose $\fg$ is a dg Lie algebra and $U$ a $\fg$-representation equipped with an $n$-shifted symplectic pairing $U\otimes U\rightarrow \CC[n]$. Consider the dg Lie algebra
\[\fh = \fg\oplus U[-1]\oplus \fg^*[n-2]\]
with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes U\rightarrow U$ given by the $\fg$-action on $U$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon U\otimes U\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_U$. The dg Lie algebra $\fh$ carries nondegenerate invariant symmetric pairing of cohomological degree $n-2$ given by pairing $\fg$ and $\fg^*$ and pairing $U$ with itself. We denote
\[U\ham \fg := B\fh.\]
This formal moduli problem is equipped with a $\Gm$-action where $\fg$ has weight 0, $U[-1]$ has weight $1$ and $\fg^*[n-2]$ has weight $2$. This may be thought of as an infinitesimal version of the Hamiltonian reduction of $U$ by the $\fg$-action.
\end{example}

Now suppose $L$ is a local $L_\infty$ algebra on a manifold $M$. For every open subset $U\subset M$ we have a formal moduli problem
\[(B L)(U) = B L(U),\]
i.e. $L$ defines a presheaf $B L$ of formal moduli problems on $M$. The following definition was introduced in \cite[Definition 4.1.3.3]{Book2}.

@@

\begin{definition}
A \defterm{classical BRST theory} on a manifold $M$ consists of the following data:
\begin{itemize}
\item A local formal moduli problem $\cM$ represented by a local $L_\infty$ algebra $L$.
\item A local functional $S_{\mr{BRST}} \in \oloc(\cM)$ of polynomial degree $\geq 2$.
\end{itemize}
Together, these data must satisfy the equation
\[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the local $L_\infty$ structure on $L$.
\end{definition}

@@

\begin{remark}
We should note here that the formal moduli problem $\cM$ appearing in the definition is a local model for the stack of BRST fields \emph{before} imposing the classical equations of motion.  This is in alignment with Remark \ref{classical_BV_from_free_BV} -- where we consider a classical BV theory and equip it with the additional data of a classical interaction -- but in contrast to the formal moduli problem occurring in Definition \ref{classical_BV_def}.
\end{remark}

@@

Given a classical BRST theory $\cM$, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_{\rm anti}$.
Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter. Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_{\rm anti}, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.

\begin{definition}
Let $(\cM, S_{\mr{BRST}})$ be a classical BRST theory. The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_{\rm anti}$.
\end{definition}

@@

\begin{remark}
In general, multiple BRST theories can give rise to the same BV theory.  A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.  Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on $F$.
\end{remark}

\begin{remark}
It is common to refer to coordinates on $\cM$ as \defterm{fields} and coordinates along the cotangent direction of $T^*[-1]\cM$ as \defterm{antifields}. Given a field $\phi$ the corresponding antifield will be denoted by $\phi^*$.
\end{remark}

>>>>

The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief, the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.  That is, given a space $\mc F$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\mc F$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \mc F \cap^h_{T^*\mc F} \Gamma_{\d S}$ of the zero section in $T^*\mc F$ with the graph of $\d S$.

The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$ as a formal moduli problem.  We will provide this motivation and interpretation from formal derived geometry in brief before proceeding to the main definitions of this section (for which an understanding of the following motivational notions is not required).

@@

\begin{remark}
We would like to emphasise that, while our definitions are motivated by formal derived geometry, all of our constructions will be formulated entirely using the language of $L_\infty$-algebras.  No knowledge of $\infty$-categories or formal derived algebraic geometry will be needed for any of the results we present in this paper, and -- indeed -- using the result of Lurie and Pridham cited above, the datum of a formal moduli problem is equivalent to the datum of an $L_\infty$ algebra.
\end{remark}

@@

\begin{example} \label{Hamiltonian_example}}
Suppose $\fg$ is a dg Lie algebra and $U$ a $\fg$-representation equipped with an $n$-shifted symplectic pairing $U\otimes U\rightarrow \CC[n]$. Consider the dg Lie algebra
\[\fh = \fg\oplus U[-1]\oplus \fg^*[n-2]\]
with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes U\rightarrow U$ given by the $\fg$-action on $U$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon U\otimes U\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_U$. The dg Lie algebra $\fh$ carries nondegenerate invariant symmetric pairing of cohomological degree $n-2$ given by pairing $\fg$ and $\fg^*$ and pairing $U$ with itself. We denote
\[U\ham \fg := B\fh.\]
This formal moduli problem is equipped with a $\Gm$-action where $\fg$ has weight 0, $U[-1]$ has weight $1$ and $\fg^*[n-2]$ has weight $2$. This may be thought of as an infinitesimal version of the Hamiltonian reduction of $U$ by the $\fg$-action.
\end{example}

Now suppose $L$ is a \emph{local} $L_\infty$ algebra on a manifold $M$. By a local $L_\infty$ algebra, we mean an $L_\infty$ algebra whose underlying graded vector space is the sheaf of sections of a graded vector bundle, where the differential and the brackets are given by polydifferential operators (see \cite[Section 3.1.3]{Book2} for a detailed definition).

\begin{remark}
The constructions given in Examples \ref{ex:tangentBg} to \ref{Hamiltonian_example} all still make sense for local $L_\infty$ algebras, although we should take some care.  Instead of using the \emph{linear} dual $\gg^*$ of a dg Lie algebra, we should always form the density-valued dual $\L^! = L^* \otimes \mr{dens}_M$ for a local $L_\infty$ algebra $L$ on a manifold $M$.
\end{remark}

For every open subset $U\subset M$ we have a formal moduli problem
\[(B L)(U) = B L(U),\]
i.e. $L$ defines a presheaf $B L$ of formal moduli problems on $M$. The following definition was introduced in \cite[Definition 4.1.3.3]{Book2}.

@@

\begin{definition}
A \defterm{classical BRST theory} on a manifold $M$ consists of the following data:
\begin{itemize}
\item A local formal moduli problem $\mc F$ represented by a local $L_\infty$ algebra $L$.
\item A local functional $S_{\mr{BRST}} \in \oloc(\mc F)$ of polynomial degree $\geq 2$.
\end{itemize}
Together, these data must satisfy the equation
\[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the local $L_\infty$ structure on $L$.
\end{definition}

@@

\begin{remark}
We should note here that the formal moduli problem $\mc F$ appearing in the definition is a local model for the stack of BRST fields \emph{before} imposing the classical equations of motion.  This is in alignment with Remark \ref{classical_BV_from_free_BV} -- where we consider a classical BV theory and equip it with the additional data of a classical interaction -- but in contrast to the formal moduli problem occurring in Definition \ref{classical_BV_def}.
\end{remark}

@@

Given a classical BRST theory $\mc F$, we may consider the cotangent theory $T^*[-1]\mc F$ whose action functional we denote by $S_{\rm anti}$.
Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\mc F\rightarrow \mc F$ by the same letter. Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\mc F)$ implies that $\{S_{\rm anti}, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\mc F)$.

\begin{definition}
Let $(\mc F, S_{\mr{BRST}})$ be a classical BRST theory. The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\mc F$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_{\rm anti}$.
\end{definition}

@@

\begin{remark}
In general, multiple BRST theories can give rise to the same BV theory.  A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} graded vector sub-bundle with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.  Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on the sub-bundle.
\end{remark}

\begin{remark}
It is common to refer to coordinates on $\mc F$ as \defterm{fields} and coordinates along the cotangent direction of $T^*[-1]\mc F$ as \defterm{antifields}. Given a field $\phi$ the corresponding antifield will be denoted by $\phi^*$.
\end{remark}

### 2022-04-15 twist_selecta_referee_comments.tex
more corrections to earlier in the paper

\begin{enumerate}
 \item Page 8: Added an explanatory comment.
 \item Page 18: \chris{I propose that the best thing to do here would be to add a longish remark on $\infty$-categories with some references, but reassuring the reader that no knowledge of details is needed to understand the content of the paper.}
 \pavel{Hmm. I would prefer not to add anything about $\infty$-categories as we are not really using them. Could be good to say that we use the equivalence as a black box: we \emph{define} FMPs as $L_\infty$ algebras. Like in Definition 1.6, how about we just give a definition ``an FMP is an $L_\infty$ algebra'' and add a remark after the definition that it is justified by the Lurie--Pridham result, but we will not be using it?}

 \item Page 20 points 1 and 2: Some further explanation was added for the notation here. \pavel{We define cotangent bundles etc of formal moduli problems, but then work with local formal moduli problems. The confusion arises because we never really defined what $T^*BL$ is when $L$ is a local $L_\infty$ algebra.}
 \item Page 20 point 3: Added a remark, thank you.
 \item Page 27: Added an additional remark here to clarify the definition.
 \brian{Maybe the issue is also with us calling this a BRST 'theory'? Perhaps less conflicting will be to refer to this as 'BRST data'. What do you think?} \chris{I don't think that's the issue, but maybe we should use a letter other than $\mathcal M$ for the formal moduli problem here.  Like maybe $\mathcal F$ for fields?}
 \pavel{Perhaps, we should just reply to the referee rather than add a remark? Agree about changing the letters though to clarify matters: the FMP he writes down is associated to BV fields, while here we have an extra data. If we change the letters, it will be easier to address the objection.}
 \item Page 29: Used $1/j$ for the root of the canonical bundle instead of $1/m$.
 \item Page 32: Clarified the condition $p^*S_N = S_M$ with a remark and fixed a small typo in the definition.
 \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here.
 \item Page 34 point 2: The parameter $\eps$ in the given equivalence corresponds to $\d z$, where $z$ is a complex coordinate on the factor $\CC$.  Because this parameter has degree 1, it is formal and the issue indicated here does not arise.
 \item Page 35: Added some clarification to the notation here.
 \item Page 36: Yes, $Q_i$ and $\lambda$ are sections of the same thing, clarified this point. \chris{rest to respond to}
 \item Page 37, point 1: We have added the clarifying adjective ``Euclidean''.
 \item Page 37, point 2: We have clarified when we are working with merely alternative algebras and when we require associativity.
 \item Page 38: We have mentioned that it is a version of the Fierz identity, thank you.
 \item Page 51: Thank you, reference added.
 \item Page 52: Thank you for the remark; we have removed the confusing sentence.
 \item Page 54: Added a reference for this claim to the relevant section of [ES].
 \item Page 56: This section was written confusingly, and we have corrected it.  Both $Q_+$ and $Q_-$ individually have stabilizers isomorphic to $\mr{SU}(4)$, and the intersection of these stabilizers is isomorphic to $\mr{SU}(3)$.
 \item Page 77: Thanks, we have corrected the confusing appearance of ``six-dimensional'' which refers to the spin group of the 6-dimensional vector space, rather than the dimension of the spin representation which is 4.
\end{enumerate}

>>>>

\begin{enumerate}
 \item Page 8: Added an explanatory comment.
 \item Page 18: As the referee very reasonably points out, we only use the notion of a formal moduli problem to provide geometric motivation for the constructions formulated within the paper.  In fact, by the cited result of Lurie and Pridham, the datum of a formal moduli problem is equivalent to that of an $L_\infty$ algebra, and all the results that we provide are presented in the latter language, so that knowledge of $\infty$-categories and derived geometry are not needed in order to understand the paper.  We added a remark (Remark 1.1) to point this out to the reader, and to reassure the reader that a detailed understanding of this motivation is not needed to understand the results of the paper.

 \item Page 20 points 1 and 2: Some further explanation was added for the notation here, along with some additional orienting comments on the introduction of local $L_\infty$ algebras.
 \item Page 20 point 3: Added a remark, thank you.
 \item Page 27: Added an additional remark here to clarify the definition.  In addition, in order to emphasise the difference here with the notation we use for the $L_\infty$ algebra of BF fields, we altered our notation to refer to the space $\mathcal F$ of BRST fields, where $\mathcal F$ is intended to suggest ``fields'', instead of using $\mathcal M$ as in the BV context. \item Page 29: Used $1/j$ for the root of the canonical bundle instead of $1/m$.
 \item Page 32: Clarified the condition $p^*S_N = S_M$ with a remark and fixed a small typo in the definition.
 \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here.
 \item Page 34 point 2: The parameter $\eps$ in the given equivalence corresponds to $\d z$, where $z$ is a complex coordinate on the factor $\CC$.  Because this parameter has degree 1, it is formal and the issue indicated here does not arise.
 \item Page 35: Added some clarification to the notation here.
 \item Page 36: Yes, $Q_i$ and $\lambda$ are sections of the same thing, clarified this point. \chris{rest to respond to}
 \item Page 37, point 1: We have added the clarifying adjective ``Euclidean''.
 \item Page 37, point 2: We have clarified when we are working with merely alternative algebras and when we require associativity.
 \item Page 38: We have mentioned that it is a version of the Fierz identity, thank you.
 \item Page 51: Thank you, reference added.
 \item Page 52: Thank you for the remark; we have removed the confusing sentence.
 \item Page 54: Added a reference for this claim to the relevant section of [ES].
 \item Page 56: This section was written confusingly, and we have corrected it.  Both $Q_+$ and $Q_-$ individually have stabilizers isomorphic to $\mr{SU}(4)$, and the intersection of these stabilizers is isomorphic to $\mr{SU}(3)$.
 \item Page 77: Thanks, we have corrected the confusing appearance of ``six-dimensional'' which refers to the spin group of the 6-dimensional vector space, rather than the dimension of the spin representation which is 4.
\end{enumerate}
